---
title: "create DSVM"
author: "Christian Hamson"
date: "May 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Do some basic work using the AzureR packages
Run the RVARusers.R script first

```{r}
library(AzureRMR)
az <- get_azure_login()
az
az$list_subscriptions()
```

Now create a VM using the AzureVM package
There are just a few images prebuilt, but you can deploy your own
template. I will use a prebuilt image for the DSVM
create a key using ssh-keygen if you don't already have one.
It isn't too horrible to have your subscription id exposed, but I've created a secret for my subscription id using the keyringr package. AzSubID is the name I've given to my subscription id

```{r}
install.packages("AzureVM")
library(AzureVM)

install.packages("keyringr")
library(keyringr)
credential_label <- "AzSubID"
credential_path <- paste(Sys.getenv("USERPROFILE"), '\\DPAPI\\passwords\\', Sys.info()["nodename"], '\\', credential_label, '.txt', sep="")
sub1 <- az$get_subscription(decrypt_dpapi_pw(credential_path))


rg <- sub1$create_resource_group("chrisDaily", location = "eastus")
rg

key <- readLines("C://Users//chhamso//.ssh//id_rsa.pub")
chrisDaily <- rg$create_vm("chrisdaily", username="chhamso", passkey=key, userauth_type="key", os="Ubuntu")
chrisDaily
```

After all the above is done you can login to your new vm via ssh or X2Go if you'd like a desktop. 
